---
name: Ben
surname: Jaques-Leslie
position: "Research and Data Scientist"
address: "3415 39th Ave South, Minneapolis, MN 55406"
phone: +1 919 928 3650
# www: benjaquesleslie.com
email: "benjaminjaques@gmail.com"
twitter: benjaminjaques
github: bpffjl
linkedin: benjaques
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 220142
docname: "Résumé"
output: vitae::awesomecv #for html markdowncv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(googlesheets4)
library(tidyverse)


edu <- read_sheet(
  "https://docs.google.com/spreadsheets/d/1q_xOb6RizwdmZ0qgTWpW-PFmfX_qXJ65kpdDH5pnxP8/edit?usp=sharing") %>% 
  arrange(desc(Year))

job <- read_sheet(
  "https://docs.google.com/spreadsheets/d/1unv9PrAeBjS2wYR7IMPw2fjf_tqER5cROWqlvuzkun8/edit?usp=sharing")

other_honors <- read_sheet(
  "https://docs.google.com/spreadsheets/d/1owCp0ptfzdbI6puUGuNjY-2B-51nNz1gDZQFxFyr2bQ/edit?usp=sharing")

prez <- read_sheet(
  'https://docs.google.com/spreadsheets/d/18ROsma6hfidvRyC3cMCGiCVHeklNchqySq2ja7zWSKQ/edit?usp=sharing'
)

other_activites <- read_sheet(
  'https://docs.google.com/spreadsheets/d/1mSqq8kenrECK86SG_skypCx477AEE2J5_FewsMwBifE/edit?usp=sharing'
)

```

# Education

```{r}
edu %>% 
  detailed_entries(Degree, Year, Institution, Where, Why) %>%
  filter(str_detect(where,"USA"))
```

# Experience

```{r}
job %>% 
  filter(year_start > 2009) %>%
  filter(!str_detect(job,"San Diego")) %>%
  filter(presentation == 0) %>% 
  filter(other_honors == 0) %>% 
  arrange(desc(year_start),
          job,
          position) %>% 
  mutate(when = 
           case_when(year_end == 'NULL' ~ glue::glue("{year_start}"),
                     TRUE ~ glue::glue("{year_start} - {year_end}")) 
           ) %>% 
  mutate(
    position = case_when(
      position == "Data Scientist" ~ glue::glue("{position} (80% time, concurrent with Research Scientist)"),
      position == "Research Scientist" ~ glue::glue("{position} (Full-time, then 20% time when concurrent with Data Scientist)"),
      TRUE ~
      glue::glue("{position} (Full-time)"),
    ),
    position = as.character(position)
  ) %>% 
  detailed_entries(
    what = position,
    when = when,
    with = job,
    where = Location,
    why = activity
  )
```

# Additional information

 * **Computer Skills**: R, SQL, Tableau, STATA, MS Office, Salesforce, SharePoint, Git, ArcGIS (limited) Python (limited), Julia (limited)
 * **International Experience**: Kenya, Morocco, Sierra Leone, China, India, South Korea, Thailand, Vietnam, Egypt, United Arab Emirates, Qatar, Brazil, Mexico, Canada, France, Italy, the Netherlands, Spain, Turkey, and UK




