---
name: Ben
surname: Jaques-Leslie
position: "Research and Data Scientist"
address: "3415 39th Ave South, Minneapolis, MN 55406"
phone: +1 919 928 3650
# www: benjaquesleslie.com
email: "benjaminjaques@gmail.com"
twitter: benjaminjaques
github: bpffjl
linkedin: benjaques
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 220142
docname: "Résumé"
output: vitae::awesomecv #for html markdowncv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(googlesheets4)
library(tidyverse)
source(here::here("functions","load_education.R"))
source(here::here("functions","load_jobs.R"))
source(here::here("functions","load_other_honors.R"))
source(here::here("functions","load_other_activities.R"))
source(here::here("functions","load_presentations.R"))
```


```{r laod, include=FALSE}
edu <- load_education() 

job <- load_jobs()

other_honors <- load_other_honors()

prez <- load_presentations()

other_activites <- load_other_activities()

```

# Education

```{r}
edu %>% 
  detailed_entries(Degree, Year, Institution, Where, Why) %>%
  filter(str_detect(where,"USA") | str_detect(where,"Virtual"))
```

# Selected experience

```{r}
job %>% 
  filter(year_start > 2015) %>%
  filter(!str_detect(job,"San Diego")) %>%
  filter(presentation == 0) %>% 
  filter(other_honors == 0) %>% 
  arrange(desc(year_start),
          job,
          position) %>% 
  mutate(when = 
           case_when(year_end == 'NULL' ~ glue::glue("{year_start}"),
                     TRUE ~ glue::glue("{year_start} - {year_end}")) 
           ) %>% 
  mutate(
    position = case_when(
      position == "Data Scientist" ~ glue::glue("{position} (80% time, concurrent with Research Scientist)"),
      position == "Research Scientist" ~ glue::glue("{position} (Full-time, then 20% time when concurrent with Data Scientist)"),
      TRUE ~
      glue::glue("{position} (Full-time)"),
    ),
    position = as.character(position)
  ) %>% 
  detailed_entries(
    what = position,
    when = when,
    with = job,
    where = Location,
    why = activity
  )
```

# Other activities

```{r}
other_activites %>% 
  arrange(desc(year_start),
          role,
          institution) %>% 
  filter(year_start > 2015) %>% 
  mutate(when = 
           case_when(year_end == 'NULL' ~ glue::glue("{year_start}"),
                     year_end == 'NA' ~ glue::glue("{year_start}"),
                     is.na(year_end) ~ glue::glue("{year_start}"),
                     TRUE ~ glue::glue("{year_start} - {year_end}")) 
           ) %>% 
  detailed_entries(
    what = role,
    when = when,
    with = institution,
    where = location,
    why = activity)
```

# Other honors

```{r}
other_honors %>% 
  detailed_entries(honor, year, institution, location, activity)
```

# Additional information

 * **Computer Skills**: R, Github, AzureDevops, SQL, STATA, MS Office, Salesforce, SharePoint, ArcGIS (limited) Python (limited), Julia (limited)
 * **International Experience**: Kenya, Morocco, Sierra Leone, China, India, South Korea, Thailand, Vietnam, Egypt, United Arab Emirates, Qatar, Brazil, Mexico, Canada, France, Italy, the Netherlands, Spain, Turkey, and UK




