---
name: Ben
surname: Jaques-Leslie
position: "Program Evaluator and Data Scientist"
address: "3415 39th Ave South, Minneapolis, MN 55406"
phone: +1 919 928 3650
# www: benjaquesleslie.com
email: "benjaminjaques@gmail.com"
twitter: benjaminjaques
github: bpffjl
linkedin: benjaques
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 220142
docname: "Résumé"
output: 
  vitae::moderncv:
    theme: "classic" #for html markdowncv
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(googlesheets4)
library(tidyverse)
source(here::here("functions","load_education.R"))
source(here::here("functions","load_jobs.R"))
source(here::here("functions","load_other_honors.R"))
source(here::here("functions","load_other_activities.R"))
source(here::here("functions","load_presentations.R"))
```

```{r laod, include=FALSE}
edu <- load_education("https://docs.google.com/spreadsheets/d/1RTMD913BsPciE3sBMtClxqrGwwbqfmdv6uQbRdX6YvQ/edit?usp=sharing") 

job <- load_jobs("https://docs.google.com/spreadsheets/d/1VEHa179hkCHgPIW5Fhvr6vMBQKvKkkGaTwkC47K04MU/edit?usp=sharing")

other_honors <- load_other_honors()

prez <- load_presentations()

other_activites <- load_other_activities()

```

# PROFESSIONAL SUMMARY

Experienced program evaluator and data scientist with 13+ years of
expertise in evaluation, organizational learning, and data analysis.
Proven track record in leading collaborative evaluation projects,
facilitating learning across diverse teams, and implementing equitable
evaluation practices. Strong background in both federal and nonprofit
sectors with demonstrated success in building evaluation capacity and
driving data-informed decision-making.

# RELEVANT EXPERIENCE

```{r, collapse=TRUE}
job %>% 
  # filter(presentation == 0) %>% 
  # filter(other_honors == 0) %>% 
  # filter(research == 1) %>% 
  # filter(primary == 'research') %>% 
  arrange(desc(year_start),
          job,
          position) %>% 
  mutate(when = 
           case_when(year_end == 'NULL' ~ glue::glue("{year_start}"),
                     TRUE ~ glue::glue("{year_start} - {year_end}")) 
           ) %>% 
  detailed_entries(
    what = position,
    when = when,
    with = job,
    where = Location,
    why = activity
  )
```

# EDUCATION

```{r}
edu %>% 
  detailed_entries(Degree, Year, Institution, Where, Why) %>% 
  filter(when < 2020)
```

# SKILLS & EXPERTISE

-   **Evaluation Methods**: Equitable evaluation practices,
    mixed-methods evaluation, performance measurement
-   **Facilitation**: Learning-focused facilitation, workshop design,
    hybrid meeting management
-   **Technical**: R, SQL, Github, Azure DevOps, Tableau, STATA
-   **Project Management**: Agile methodologies, collaborative project
    leadership
-   **Communications**: Technical writing, data visualization,
    stakeholder engagement

# RELEVANT TRAINING

```{r}
edu %>% 
  detailed_entries(Degree, Year, Institution, Where, Why) %>% 
  filter(when >= 2020)
```

# PUBLICATIONS & PRESENTATIONS

Selected recent works focused on evaluation and organizational learning:

-    "The effects of remote designation on applications and selections
    to federal government jobs" (2025)

-    "Using Program Success Metrics and Organizational Change Principles
    to Implement Responsive and Modernized TANF Programs" (2023)

-    "Centering Racial Equity in TANF Data Use" (2022)
